`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-17 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
random typo correction

\begin{table}[h!]\footnotesize
    \begin{tabular}{rl}
        $V(\nu)$ & Spectrum of the dynamic field \\
	$\nu$ & Spatial frequency \\
	$\nu_c$ & Spatial cut-off frequency \\
	$\Delta_s$ & Distance between adjacent sensors \\
	$\rho$ & Over-sampling parameter \\
	$\Delta_b$ & Distance between field basis functions \\
	$\sigma_{nu}^2$ & Variance of FT of Gaussian basis function \\
	$\sigma^2$ & Spatial variance of Gaussian in spatial domain \\
    \end{tabular}
    \caption{Frequency Analysis}
\end{table}

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	    $\chi$ & Matrix of sigma vectors \\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix
    \end{tabular}
    \caption{State Estimation}
\end{table}

>>>>

\begin{table}[h!]\footnotesize
    \begin{tabular}{rl}
        $V(\nu)$ & Spectrum of the dynamic field \\
	$\nu$ & Spatial frequency \\
	$\nu_c$ & Spatial cut-off frequency \\
	$\Delta_y$ & Distance between adjacent sensors \\
	$\rho$ & Over-sampling parameter \\
	$\Delta_{\phi}$ & Distance between field basis functions \\
	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
    \end{tabular}
    \caption{Frequency Analysis}
\end{table}

\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\hat{\mathbf{x}}$ & State estimate \\
	$\chi$ & Matrix of sigma vectors \\
    	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
    	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
    	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
    	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
    	$P^f_t$ & Forward posterior covariance matrix \\
    	$P^{f-}_t$ & Forward prior covariance matrix \\
    	$P^b_t$ & Backward posterior covariance matrix \\
    	$P^{b-}_t$ & Backward prior covariance matrix \\
	$\mathcal K_{t} $& Filter gain\\
	$M_t$& Cross-covariance matrix\\
	$S_t$& Smoother gain
    \end{tabular}
    \caption{State Estimation}
\end{table}
